Investigating Cross-Sectional Size Distribution of Randomly Distributed 3D Spheres

### 2020-09-03 Paper/main.tex
Changed location of figures for paper

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/box3d.pdf}
\caption{$750$ spheres of radius 0.7 distributed randomly in a cube of length 20,
  such that no sphere is touching or overlapping another sphere. A horizontal
  plane, in blue, passes through the box and ``cuts'' through the
  spheres.}\label{fig:3dplot_plane}
\end{center}
\end{figure}

@@

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/circles.pdf}
\caption{Planar cross-section constructed using mock data. Spheres cut by the
  plane appear as circles on the plane, with radius dependent on the relative
  position of the spheres to the plane. This distribution of the radii of the
  circles can be modelled.}\label{fig:circles}
\end{center}
\end{figure}

@@

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_01.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $0.1$
  each. There are relatively few points since the spheres are small, so there is
  relatively small chance that they will be cut by the plane. So only a few
  circles are visible on the plane. The theoretical distribution is shown, with
  the experimental data matching this distribution, showing a slow increase in
  number or circles as radius increases.}\label{fig:size1}
\end{center}
\end{figure}

@@

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_03.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $0.3$
  each. Compared to Figure~\ref{fig:size1}, there are many more experimental data
  points, since it is more likely that the plane will intersect these larger
  spheres. The experimental data more clearly resembles the theoretical
  distribution, showing a strong increase in number of circles as radius
  increases towards the maximum of 0.3.}\label{fig:size3}
\end{center}
\end{figure}

@@

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_07.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
  each. We do not observe much difference in how well the experimental data
  resembles the theoretical distribution between this figure and
  Figure~\ref{fig:size3}. With larger sized spheres, the simulation becomes harder
  to run as it is more difficult to randomly place spheres in a finite space
  without overlap.}\label{fig:size7}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{./../Figures/750_07_random.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $R$
  where $0.65 < R < 0.75$. The theoretical distribution is now different,
  although the experimental data still resembles this new distribution, showing
  a maximum around $R = 0.7$ and a sharp decrease after this. This is likely
  because there are more spheres with radii such that an overlap between $0$ and
  $0.7$ is possible, and relatively few spheres with radii such that a larger
  overlap is possible.}
\label{fig:random}
\end{center}
\end{figure}

\begin{figure*}[ht!]
  \centering
  \subfloat[Noise 2 orders of magnitude smaller than radius]
  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_100.pdf}
  \label{fig:2noise}}
  \centering
  \subfloat[Noise 1 order of magnitude smaller than radius]
  {\includegraphics[width=0.45\textwidth]{./../Figures/750_07_Noise_10.pdf}
  \label{fig:1noise}}
  \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
    each. Each recorded radius has a random noise added to it in order to
    determine how sensitive the data is to experimental
    error. Figure~\ref{fig:2noise} shows the distribution for an added noise 2
    orders of magnitude smaller than the recorded radius, while
    Figure~\ref{fig:1noise} is the same for noise 1 order of magnitude smaller. As
    we can see, the experimental data very resembles the theoretical
    distribution when noise of 2 orders of magnitude smaller are added. But this
    is not true when noise of 1 order of magnitude smaller is added, implying
    the data is very sensitive to experimental data.}
  \label{fig:noiseplots}
\end{figure*}

>>>>

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{images/box3d.pdf}
\caption{$750$ spheres of radius 0.7 distributed randomly in a cube of length 20,
  such that no sphere is touching or overlapping another sphere. A horizontal
  plane, in blue, passes through the box and ``cuts'' through the
  spheres.}\label{fig:3dplot_plane}
\end{center}
\end{figure}

@@

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{images/circles.pdf}
\caption{Planar cross-section constructed using mock data. Spheres cut by the
  plane appear as circles on the plane, with radius dependent on the relative
  position of the spheres to the plane. This distribution of the radii of the
  circles can be modelled.}\label{fig:circles}
\end{center}
\end{figure}

@@

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{images/750_01.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $0.1$
  each. There are relatively few points since the spheres are small, so there is
  relatively small chance that they will be cut by the plane. So only a few
  circles are visible on the plane. The theoretical distribution is shown, with
  the experimental data matching this distribution, showing a slow increase in
  number or circles as radius increases.}\label{fig:size1}
\end{center}
\end{figure}

@@

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{images/750_03.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $0.3$
  each. Compared to Figure~\ref{fig:size1}, there are many more experimental data
  points, since it is more likely that the plane will intersect these larger
  spheres. The experimental data more clearly resembles the theoretical
  distribution, showing a strong increase in number of circles as radius
  increases towards the maximum of 0.3.}\label{fig:size3}
\end{center}
\end{figure}

@@

\begin{figure}%[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{images/750_07.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
  each. We do not observe much difference in how well the experimental data
  resembles the theoretical distribution between this figure and
  Figure~\ref{fig:size3}. With larger sized spheres, the simulation becomes harder
  to run as it is more difficult to randomly place spheres in a finite space
  without overlap.}\label{fig:size7}
\end{center}
\end{figure}

\begin{figure}[H]%[!ht]
\begin{center}
\includegraphics[width=0.45\textwidth]{images/750_07_random.pdf}
\caption{Distribution of circle radii on plane for $750$ spheres of radius $R$
  where $0.65 < R < 0.75$. The theoretical distribution is now different,
  although the experimental data still resembles this new distribution, showing
  a maximum around $R = 0.7$ and a sharp decrease after this. This is likely
  because there are more spheres with radii such that an overlap between $0$ and
  $0.7$ is possible, and relatively few spheres with radii such that a larger
  overlap is possible.}
\label{fig:random}
\end{center}
\end{figure}

\begin{figure*}[ht!]
  \centering
  \subfloat[Noise 2 orders of magnitude smaller than radius]
  {\includegraphics[width=0.45\textwidth]{images/750_07_Noise_100.pdf}
  \label{fig:2noise}}
  \centering
  \subfloat[Noise 1 order of magnitude smaller than radius]
  {\includegraphics[width=0.45\textwidth]{images/750_07_Noise_10.pdf}
  \label{fig:1noise}}
  \caption{Distribution of circle radii on plane for $750$ spheres of radius $0.7$
    each. Each recorded radius has a random noise added to it in order to
    determine how sensitive the data is to experimental
    error. Figure~\ref{fig:2noise} shows the distribution for an added noise 2
    orders of magnitude smaller than the recorded radius, while
    Figure~\ref{fig:1noise} is the same for noise 1 order of magnitude smaller. As
    we can see, the experimental data very resembles the theoretical
    distribution when noise of 2 orders of magnitude smaller are added. But this
    is not true when noise of 1 order of magnitude smaller is added, implying
    the data is very sensitive to experimental data.}
  \label{fig:noiseplots}
\end{figure*}
